Characterization and Photometric Performance of the Hyper Suprime-Cam Software Pipeline.

### 2017-04-24 draft/ms_v4.tex
cModel mag

    In Fig \ref{fig:cmodel_mag}, we illustrate the photometric uncertainties of the
    \cmodel{} magnitudes in each band using the same format as
    Fig \ref{fig:psf_mag}.

    The overall performance of \cmodel{} photometry is very reasonable all the way
    down to $i_{\mathrm{Input}}=25.2$ mag.
    Compared to the qualities of PSF photometry for stars, the magnitude differences
    of \cmodel{} show much larger scatter for galaxies.
    Given the diversity of properties of these galaxies and the complexities in the
    model-fitting process, this difference is expected.
    At the same time, we can see that the \cmodel{} algorithm in \hscpipe{} can
    provide unbiased and consistent photometry for galaxies in different bands and
    seeing conditions.

    In $i$-band, the median flux uncertainty of the \forced{} \cmodel{} is ${\sim}7$\%
    in the good-seeing \tract{} at $i_{\mathrm{Input}}{\sim}20.0$ mag,
    and ${\sim}9$\% at $i_{\mathrm{Input}}{\sim}24.0$ mag.
    Down to $i_{\mathrm{Input}}{\sim}25.0$ mag, the median uncertainty maintains
    at ${\sim}11$\% level.
    For the bad-seeing \tract{} in $i$-band, the performance is very similar.
    From $i_{\mathrm{Input}}{\sim}20.0$ to $25.0$ mag, the median magnitude difference
    between output and input values changes from \plus{}$0.041$ mag to
    \minus{}$0.005$ mag, which suggests that \forced{} \cmodel{} photometry is
    unbiased down to the very faint end.
    It is worth noting that the photometric uncertainties estimated by \synpipe{}
    are significantly larger than the fiducial error from \hscpipe{}, which does not
    take into account the systematic uncertainties involved in the modeling
    fitting process.
    Although the synthetic galaxies in our sample are described by the simple single-\ser{}
    model, the\cmodel{} algorithm can only approximate them to a certain accuracy,
    especially when the noise level, deblending uncertainty, and priors of model
    parameters are considered.
    Given that real galaxies are more complex in structural details, these
    uncertainties should be treated as lower limits.

    The performance of \forced{} \cmodel{} photometry is very consistent across all
    filters.
    For $g$-, $r$-, and $z$-bands, the photometric uncertainties are very similar to
    the ones for $i$-band between $20.0$ and $25.0$ mag.
    The \forced{} \cmodel{} magnitudes are also unbiased for these three filters
    across the entire input magnitude range.
    The uncertainties for $y$-band are slightly larger, ranging from 9\% to 17\% in the
    same magnitude bins.
    In addition, the \forced{} \cmodel{} tends to overestimate the total flux in $y$-band
    at $y_{\mathrm{Input}}>24.0$ mag.
    Mean magnitude differences change from \minus{}0.06 at 24.0 mag to \minus{}0.22
    mag at 25.0 mag.
    Both a worse seeing condition and a higher background noise level can make it more
    difficult to detect a faint object on a $y$-band image.
    At $y_{\mathrm{Input}}{\sim}24.0$, the average \s2n{} for \cmodel{} in $y$-band
    is already close to the detection threshold.

    As mentioned, the statistics for brighter galaxies are very uncertain due to the
    small sample size.
    However, we do notice that, at $i_{\mathrm{Input}}<20.0$, the \forced{}
    \cmodel{} photometry shows larger uncertainty and starts to systematically
    underestimate the total flux.
    This problem is confirmed via comparing with more carefully derived total fluxes
    for bright galaxies (e.g., \citealt{HSCDR1}, Huang\etal in prep.).
    It relates to the known issues of \hscpipe{} (e.g., \hscpipe{}over-deblends around bright objects; inappropriately weights priors in \cmodel{}); but it may also suggest
    that, at the imaging depth of HSC, assumptions in \cmodel{} are no longer the
    best choice in modeling these galaxies (e.g., for massive elliptical galaxies;
    see Huang\etal in prep.~for more details).

    For the highly blended synthetic galaxies, we also see systematically
    underestimated total flux (average offset ${\sim}0.1$ mag) and larger scatter
    of photometric uncertainty in all five bands.
    Meanwhile, the contrast between relatively isolated and highly blended galaxies
    in photometric performance is not as staggering as the one for synthetic
    stars (Fig \ref{fig:psf_mag}).

    We also test the \unforced{} \cmodel{} photometry in all five bands, and the
    results suggest similar accuracies.
    We highlight the differences between \forced{} and \unforced{} \cmodel{}
    photometry in $g$- and $y$-bands in Fig \ref{fig:cmodel_diff}.
    The only noticeable difference is for galaxies brighter than $24.0$ mag in
    $g$-band; their \forced{} \cmodel{} magnitudes are systematically brighter than
    the \unforced{} ones.

>>>>

    In Fig \ref{fig:cmodel_mag}, we illustrate the photometric uncertainties of the
    \cmodel{} magnitudes in each band using the same format for Fig \ref{fig:psf_mag}.

    The overall performance of \cmodel{} photometry is reasonable down to 
    $i_{\mathrm{Input}}=25.2$ mag.
    Compared to PSF photometry for stars, the uncertainties of \cmodel{} show larger 
    scatter for galaxies, which is expected given the diversity of structural 
    properties and complexities in the model-fitting process.
    At the same time, \cmodel{} algorithm in \hscpipe{} provides unbiased and consistent 
    photometry for galaxies in different bands and seeing conditions.

    In $i$-band, the typical flux accuracy for \forced{} \cmodel{} is ${\sim}7-9$\%
    in the good-seeing \tract{} at $i_{\mathrm{Input}}<24.0$ mag, and moderately 
    decreases to ${\sim}11$\% at $25.0$ mag.
    and ${\sim}9$\% at $i_{\mathrm{Input}}{\sim}24.0$ mag.
    For the bad-seeing \tract{} in $i$-band, the performance is very similar.
    At $20.0 < i_{\mathrm{Input}} < 25.0$ mag, the median magnitude offset
    between output and input values changes from \plus{}$0.041$ mag to
    \minus{}$0.005$ mag, which suggests that \forced{} \cmodel{} photometry is
    unbiased down to the very faint end.

    It is worth noting that the flux uncertainty from \synpipe{} is significantly 
    larger than the flux error from \hscpipe{}, which does not take into account the 
    systematic uncertainties involved in the modeling fitting process.
    Although the synthetic galaxies here are described by simple single-\ser{} model, 
    \cmodel{} algorithm can only approximate them to certain accuracy, especially when 
    background noise, deblending uncertainty, and priors of model parameters are 
    considered.
    Given that real galaxies are more complex in structure, these uncertainties should 
    be treated as lower limits.

    The accuracy of \forced{} \cmodel{} photometry is consistent across all filters.
    For $g$, $r$, and $z$ bands, the photometric uncertainties are very similar to
    $i$-band results between $20.0$ and $25.0$ mag.
    The \forced{} \cmodel{} magnitudes are also unbiased for these three filters
    across the entire input magnitude range.
    The uncertainties for $y$ band are slightly worse, ranging from 9\% to 17\% in the
    same magnitude bins.
    In addition, the \forced{} \cmodel{} tends to overestimate the total flux in 
    $y$ band at $>24.0$ mag.
    Average magnitude offsets change from \minus{}0.06 at $24.0$ mag to \minus{}0.22
    mag at 25.0 mag.
    Both a worse seeing condition and a higher background noise level can make it more
    difficult to detect faint object in $y$ band.
    At $y_{\mathrm{Input}}{\sim}24.0$, the average \s2n{} for \cmodel{} is already
    around the detection threshold.

    As mentioned, the statistics for brighter galaxies are uncertain due to small 
    sample size.
    We do notice that, at $i_{\mathrm{Input}}<20.0$, the \forced{} \cmodel{} photometry 
    shows larger uncertainty and starts to systematically underestimate the total flux.
    Based on external comparisons, the behavior of \cmodel{} for bright galaxies may 
    depend on the galaxy type (e.g., \citealt{HSCDR1}). 
    Known issues of current \hscpipe{} (e.g., \hscpipe{} over-deblends around bright 
    objects; inappropriately weights priors in \cmodel{}) could lead to poorer 
    photometric quality for bright galaxies. 
    Meanwhile, at the imaging depth of HSC ($>29.0$\sb{} in $i$ band for Wide layer), 
    assumptions in \cmodel{} may no longer be the best choice for modeling bright 
    galaxies (e.g., for massive elliptical galaxies; see Huang\etal in prep.~for 
    more details).
    We will look into these issues more carefully in the future.

    For the highly blended galaxies, we also see systematically underestimated total 
    flux (average offset ${\sim}0.1$ mag) and larger scatter of photometric 
    uncertainty in all five bands.
    Meanwhile, the contrast between relatively isolated and highly blended galaxies
    in photometric performance is not as staggering as the one for synthetic
    stars (Fig \ref{fig:psf_mag}).

    We also test the \unforced{} \cmodel{} photometry in all five bands, and the
    results suggest similar accuracies.
    We highlight the differences between \forced{} and \unforced{} \cmodel{}
    photometry in $g$ and $y$ bands in Fig \ref{fig:cmodel_diff}.
    The only noticeable feature is for galaxies brighter than $24.0$ mag in
    $g$ band, the \forced{} \cmodel{} magnitudes are systematically brighter than
    the \unforced{} ones, suggesting \forced{} \cmodel{} shows better accuracy in 
    $g$ band.
